---
title: "607 HW1"
author: "Samane Khademi"
date: "2022-08-26"
output: html_document
---

# Why Many Americans Don't Vote.
Data presented here comes from polling done by Ipsos for FiveThirtyEight, using Ipsos’s KnowledgePanel, a probability-based online panel that is recruited to be representative of the U.S. population.The poll was conducted SEptamber 2019 among a sample of U.S. citizens that oversampled young, Black and Hispanic respondents, with 8,327 respondents.

Data set can be found [here](https://raw.githubusercontent.com/fivethirtyeight/data/master/non-voters/nonvoters_data.csv)

Related article can be found
[here](https://projects.fivethirtyeight.com/non-voters-poll-2020-election/)
Based on this article, In any given election, between 35 and 60 percent of eligible voters don’t cast a ballot. They think voting doesn’t matter(one missed vote isn’t going to change anything) or isn’t worth their time.

# Load Libraries  
```{r}
library(RCurl)
library(ggplot2)
```
# Import file

```{r}
x <- getURL("https://raw.githubusercontent.com/fivethirtyeight/data/master/non-voters/nonvoters_data.csv")

df <- data.frame(read.csv(text = x))
dim(df)
``` 
```{r}
head(df)
```
# Subseting:  
```{r}
df_new <- df[,c("educ","race","gender","income_cat","voter_category")]
head(df_new)
```
# Let's classify voters based on some factors:

### Does educational level has effect on voting behavior?  
```{r}
ggplot(df_new, 
       aes(x = educ, 
           fill = voter_category)) + 
  geom_bar(position = "stack")
```

## How is voting in different races?


```{r}
ggplot(df_new, 
       aes(x = race, 
           fill = voter_category)) + 
  geom_bar(position = "stack")

```

## Voting behavior based on gender:  

```{r}
ggplot(df_new, 
       aes(x = gender, 
           fill = voter_category)) + 
  geom_bar(position = "stack")
```

## Income level Vs. Voting:  

```{r}
ggplot(df_new, 
       aes(x = income_cat, 
           fill = voter_category)) + 
  geom_bar(position = "stack")
```
